%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\href{https://cs.umd.edu/}
{\textbf{Department of Computer Science}}
University of Maryland
\hfill

\GapNoBreak
\hspace{1em} Teaching Assistant for CMSC330: Organization of Programming Languages
\hfill
Fall 2016

\GapNoBreak
\href{https://www.tenable.com/}
{\textbf{Tenable Network Security}},
Columbia, MD

\GapNoBreak
\hspace{1em} Software Engineer Intern, Passive Vulnerability Scanner (PVS) Core Team
\hfill
Summer 2016
\begin{detail}
\SubBulletItem
Increased PVS engine realtime packet processing speed by 35\% by redesigning and implementing an optimized plugin evaluation algorithm.
\SubBulletItem
Designed a classifier to detect anomalous apps by system call behavior; model yielded >95\% test accuracy.
\SubBulletItem
Developed and tested a benchmarking suite to locate bottlenecks in PVS data structures.
\end{detail}

\Gap
\href{https://www.ngc.com/}
{\textbf{Northrop Grumman Information Systems}},
Annapolis Junction, MD

\GapNoBreak
\hspace{1em} 
Software Engineer Intern, APPIA \& CSAWS Platforms
\hfill
June 2015 - Apr 2016
\begin{detail}
\SubBulletItem
Contributed several UI enhancements and various Java JBoss backend bugfixes for both platforms.
\SubBulletItem
Practiced Agile \& Scrum in 3 week sprints throughout the semester.
\SubBulletItem
Developed an IRC bot for the APPIA REST API in Ruby; Created automation scripts in Python.
\end{detail}

\GapNoBreak
\hspace{1em} 
Systems Engineer Intern, Cyber Security Operations Center (CSOC)
\hfill
June 2012 - May 2015
\begin{detail}
\SubBulletItem
Developed LDAP aggregation infrastructure for >80k users, currently deployed on CSOC production servers.
\SubBulletItem
Created and developed a beta analyst threat sharing webapp in Django.
\end{detail}
